---
title: "20220517_NetworkUpdates"
author: "Sophia Anner"
date: "5/17/2022"
output: html_document
---

#Rhagoletis Mating Network Project Updates
##Sophia Anner and David Zonana
### This document serves as the most up to date work we have done to this code so far, in a "clean" version without other attemps at getting things to work. Eventually this could feasibly turn into our final code.

```{r install packages}
library(tidyverse)
library(igraph)
library(ggplot2)
library(bipartite)
```


```{r Load mating interactions data}
rhag_edges <- read.csv(file = "20220516_RhagMatingFixedDuplicates_intxns.csv", header = T)

#take out the between sex trials (there were so few and it wasn't the focus of this project, so they're not relevant to keep in)
rhag_edges <- rhag_edges %>% filter(within_sex == "N")

#change the trial names to a factor, and then to a number so we have a new column (trial_number) that gives each trial a unique number ID 1 through 25
str(rhag_edges)
rhag_edges$trial_number <- as.numeric(as.factor(rhag_edges$trial_name))

#add M and F to actor and receiver codes so they have unique IDs
rhag_edges <- rhag_edges %>% unite(receiver_uniqueID, "receiver_code", "receiver_sex", remove = F)
rhag_edges <- rhag_edges %>% unite(actor_uniqueID, "actor_code", "actor_sex", remove = F)

#create a new column for weight and fill it with ones
rhag_edges$weight <- rep(1, nrow(rhag_edges))

#reorder the edges so that actor and receiver are in the front. also, we removed columns we don't need.
rhag_edges <- rhag_edges[,c("actor_uniqueID", "receiver_uniqueID", "within_pop", "successful_copulation", "trial_number", "trial_name", "duration", "weight")]
```


```{r load data for all flies in trials}
rhag_nodes <- read.csv(file = "20220516_RhagMatingFixedDuplicates_allflies.csv", header = T)

#create a unique ID for each fly in each trial
rhag_nodes <- unite(rhag_nodes, unique_ID, "mark_code", "sex", remove = F)
```

## Here, we have a full visualization of all 25 networks using the plotweb() function in the bipartite package. 

```{r Visualize the interactions}
#create blank lists to put outputs into
incidence_mats <- list()
igraph_nets <- list()

#In this for loop, we first make igraph objects for each of the 25 trials. then, we add in edge attributes (weight and successful copulation) and node attributes (sex and host). Finally, we create incidence matrices for each igraph object, which is our matrix with females on one axis and males on the other. We will use the incidence matrices in the next for loop.
for(i in 1:25){
#make sub edge list for each trial number
sub_edge <- rhag_edges[rhag_edges$trial_number == i,]
sub_edge <- sub_edge %>% 
  group_by(actor_uniqueID, receiver_uniqueID) %>% 
  mutate(weight = sum(weight)) %>% 
  unique()
sub_node <- rhag_nodes[rhag_nodes$trial_name %in% sub_edge$trial_name,]
sub_graph <- graph_from_data_frame(d = sub_edge, vertices = sub_node$unique_ID, directed = T)
V(sub_graph)$host <- ifelse(sub_node$host == "App","lightgoldenrod1", "salmon")
V(sub_graph)$type <- as.logical(ifelse(sub_node$sex == "F", TRUE, FALSE))
igraph_nets[[i]] <- sub_graph
sub_incidence <- get.incidence(sub_graph, attr = "weight")
incidence_mats[[i]] <- sub_incidence
} 


#Next, we use the incidence matrices in the plotweb function to visualize our 25 networks. First, we sort them by decreasing row/column totals so the flies who didn't mate are grouped to the right. Then we set the color the nodes (and their borders) to match the host attribute, which was set in the first forloop.
for(i in 1:25){
  incidence_mats[[i]] <- sortweb(incidence_mats[[i]], sort.order="dec")
  plotweb(incidence_mats[[i]], method="normal", empty = F,
        col.high = V(igraph_nets[[1]])$host[match(colnames(incidence_mats[[1]]), V(igraph_nets[[1]])$name)], 
          col.low = V(igraph_nets[[1]])$host[match(rownames(incidence_mats[[1]]), V(igraph_nets[[1]])$name)],
  bor.col.high = V(igraph_nets[[1]])$host[match(colnames(incidence_mats[[1]]), V(igraph_nets[[1]])$name)],
  bor.col.low = V(igraph_nets[[1]])$host[match(rownames(incidence_mats[[1]]), V(igraph_nets[[1]])$name)])
}

```


## We have also started to take a look at some network-wide metrics. 

### *Density* = number of edges that exists divided by the total number of possible edges, so the number of matings our of all possible combinations of flies. 
### *Strength* = sum of the interactions for each fly. At this level, it would be the average number of matings for each fly in the network. 


```{r extract density and strengths}
#initialize a vector to store results in the loop, otherwise it will just write it over
densities <- rep(0, 25)
strengths <- rep(0, 25)

#use a for loop to calculate densities and strengths
for(i in 1:25){
  sub <- rhag_edges[rhag_edges$trial_number == i,]
  sub_node <- rhag_nodes[rhag_nodes$trial_name == sub$trial_name,]
  sub <- sub %>% select(actor_uniqueID, receiver_uniqueID)
  sub_graph <- graph_from_data_frame(d = sub, vertices = sub_node$unique_ID, directed = T)
  E(sub_graph)$weight <- 1
  sub_graph <- simplify(sub_graph, edge.attr.comb=list(weight="sum"))
  densities[[i]] <- edge_density(sub_graph)
  #the ith value in our density vector we made earlier, put in the edge density for each network
  strengths[[i]] <- mean(igraph::strength(sub_graph))
}  

#Note: I needed to add in igraph:: before strength because it does not work with if the bipartite package is loaded. it gives the error message x must be an array of at least two dimensions

#make a vector of trial names
trial_names <- unique(rhag_edges$trial_name)

#make a vector of temperatures
temp <- rep(c("control","warm"),times=c(10,15))

#combine into a data frame
global_summary <- data.frame(trial_names, temp, densities, strengths)


```

