---
title: "20220517_NetworkUpdates"
author: "Sophia Anner"
date: "5/17/2022"
output: html_document
---

#Rhagoletis Mating Network Project Updates
##Sophia Anner and David Zonana
### This document serves as the most up to date work we have done to this code so far, in a "clean" version without other attemps at getting things to work. Eventually this could feasibly turn into our final code.

```{r install packages}
library(tidyverse)
library(igraph)
library(ggplot2)
```


```{r Load mating interactions data}
rhag_edges <- read.csv(file = "20220516_RhagMatingFixedDuplicates_intxns.csv", header = T)

#take out the between sex trials (there were so few and it wasn't the focus of this project, so they're not relevant to keep in)
rhag_edges <- rhag_edges %>% filter(within_sex == "N")

#change the trial names to a factor, and then to a number so we have a new column (trial_number) that gives each trial a unique number ID 1 through 25
str(rhag_edges)
rhag_edges$trial_number <- as.numeric(as.factor(rhag_edges$trial_name))

#add M and F to actor and receiver codes so they have unique IDs
rhag_edges <- rhag_edges %>% unite(receiver_uniqueID, "receiver_code", "receiver_sex", remove = F)
rhag_edges <- rhag_edges %>% unite(actor_uniqueID, "actor_code", "actor_sex", remove = F)
```


```{r load data for all flies in trials}
rhag_nodes <- read.csv(file = "20220516_RhagMatingFixedDuplicates_allflies.csv", header = T)

#create a unique ID for each fly in each trial
rhag_nodes <- unite(rhag_nodes, unique_ID, "mark_code", "sex", remove = F)
```

## Here, we have a full visualization of all 25 networks, but **we still need to find a way to make this bipartite instead of a circle.** 

### The blue are females and the orange are males. The circles are apple flies, and the squares are hawthorn flies. 

```{r visualize the interactions}
par(mfrow=c(5,5))
par(mar = c(0.5,0.5,0.5,0.5))
for(i in 1:25){
  sub <- rhag_edges[rhag_edges$trial_number == i,]
  sub_node <- rhag_nodes[rhag_nodes$trial_name == sub$trial_name,]
  sub <- sub %>% select(actor_uniqueID, receiver_uniqueID)
  sub_graph <- graph_from_data_frame(d = sub, vertices = sub_node$unique_ID, directed = T)
  E(sub_graph)$weight <- 1
  sub_graph <- simplify(sub_graph, edge.attr.comb=list(weight="sum"))
  V(sub_graph)$color <- ifelse(sub_node$sex == "F", "lightblue", "orange")
  V(sub_graph)$host <- ifelse(sub_node$host == "App", "circle", "square")
  plot.igraph(sub_graph, 
              vertex.shape=V(sub_graph)$host, 
              vertex.size = 20, 
              edge.arrow.size = 0.2, 
              vertex.label.cex = 0.5, 
              edge.width = E(sub_graph)$weight*2, 
              vertex.color = V(sub_graph)$color,
              edge.color = "black")
} 
```


## We have also started to take a look at some network-wide metrics. 

### *Density* = number of edges that exists divided by the total number of possible edges, so the number of matings our of all possible combinations of flies. 
### *Strength* = sum of the interactions for each fly. At this level, it would be the average number of matings for each fly in the network. 


```{r extract density and strengths}
#initialize a vector to store results in the loop, otherwise it will just write it over
densities <- rep(0, 25)
strengths <- rep(0, 25)

#use a for loop to calculate densities and strengths
for(i in 1:25){
  sub <- rhag_edges[rhag_edges$trial_number == i,]
  sub_node <- rhag_nodes[rhag_nodes$trial_name == sub$trial_name,]
  sub <- sub %>% select(actor_uniqueID, receiver_uniqueID)
  sub_graph <- graph_from_data_frame(d = sub, vertices = sub_node$unique_ID, directed = T)
  E(sub_graph)$weight <- 1
  sub_graph <- simplify(sub_graph, edge.attr.comb=list(weight="sum"))
 # V(sub_graph)$type <- V(sub_graph)$name %in% sub$actor_code
  densities[[i]] <- edge_density(sub_graph)
  #the ith value in our density vector we made earlier, put in the edge density for each network
  strengths[[i]] <- mean(strength(sub_graph))
}  

#make a vector of trial names
trial_names <- unique(rhag$trial_name)

#make a vector of temperatures
temp <- rep(c("control","warm"),times=c(10,15))

#combine into a data frame
global_summary <- data.frame(trial_names, temp, densities, strengths)

```

