---
title: "20220517_NetworkUpdates"
author: "Sophia Anner"
date: "5/17/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Rhagoletis Mating Network Project Updates
##Sophia Anner and David Zonana
### This document serves as the most up to date work we have done to this code so far, in a "clean" version without other attemps at getting things to work. Eventually this could feasibly turn into our final code.

```{r install packages}
library(tidyverse)
library(igraph)
library(ggplot2)
```


```{r Load mating interactions data}
rhag_edges <- read.csv(file = "20220516_RhagMatingFixedDuplicates_intxns.csv", header = T)

#take out the between sex trials (there were so few and it wasn't the focus of this project, so they're not relevant to keep in)
rhag_edges <- rhag_edges %>% filter(within_sex == "N")

#change the trial names to a factor, and then to a number so we have a new column (trial_number) that gives each trial a unique number ID 1 through 25
str(rhag_edges)
rhag_edges$trial_number <- as.numeric(as.factor(rhag_edges$trial_name))

#add M and F to actor and receiver codes so they have unique IDs
rhag_edges <- rhag_edges %>% unite(receiver_uniqueID, "receiver_code", "receiver_sex", remove = F)
rhag_edges <- rhag_edges %>% unite(actor_uniqueID, "actor_code", "actor_sex", remove = F)

rhag_edges <- rhag_edges[,c(3,7,1,2,5,6,9,10,11,12,13,14,15,16)]
```


```{r load data for all flies in trials}
rhag_nodes <- read.csv(file = "20220516_RhagMatingFixedDuplicates_allflies.csv", header = T)

#create a unique ID for each fly in each trial
rhag_nodes <- unite(rhag_nodes, unique_ID, "mark_code", "sex", remove = F)

rhag_nodes <- rhag_nodes[,c(7,1,2,3,4,5,6,8,9,10,11,12)]
```

## Here, we have a full visualization of all 25 networks, but **we still need to find a way to make this bipartite instead of a circle.** 

### The blue are females and the orange are males. The circles are apple flies, and the squares are hawthorn flies. 

```{r visualize the interactions}
incidence_mats <- list()
igraph_nets <- list()

# par(mfrow=c (5,5))
# par(mar = c(0.5,0.5,0.5,0.5))
for(i in 1:25){
sub_edge <- rhag_edges[rhag_edges$trial_number == i,]
sub_node <- rhag_nodes[rhag_nodes$trial_name %in% sub_edge$trial_name,]
sub <- sub_edge %>% select(actor_uniqueID, receiver_uniqueID)
sub_graph <- graph_from_data_frame(d = sub, vertices = sub_node$unique_ID, directed = T)
E(sub_graph)$weight <- 1
sub_graph <- simplify(sub_graph, edge.attr.comb=list(weight="sum"))
set_edge_attr(sub_graph, name = "successful_copulation", value = sub_edge$successful_copulation)
V(sub_graph)$sex <- ifelse(sub_node$sex == "F", "circle", "square")
V(sub_graph)$host <- ifelse(sub_node$host == "App","lightblue", "orange")
V(sub_graph)$type <- as.logical(ifelse(sub_node$sex == "F", TRUE, FALSE))
igraph_nets[[i]] <- sub_graph
sub_incidence <- get.incidence(sub_graph, attr = "weight")
incidence_mats[[i]] <- sub_incidence
} 

edge_attr(igraph_nets[[1]])

for(i in 1:25){
incidence_mats[[i]] <- sortweb(incidence_mats[[i]], sort.order="dec")
}


for(i in 1:25){
  plotweb(incidence_mats[[i]], method="normal", empty = F,
        col.high = V(igraph_nets[[1]])$host[match(colnames(incidence_mats[[1]]), V(igraph_nets[[1]])$name)], 
          col.low = V(igraph_nets[[1]])$host[match(rownames(incidence_mats[[1]]), V(igraph_nets[[1]])$name)],
  bor.col.high = V(igraph_nets[[1]])$host[match(colnames(incidence_mats[[1]]), V(igraph_nets[[1]])$name)],
  bor.col.low = V(igraph_nets[[1]])$host[match(rownames(incidence_mats[[1]]), V(igraph_nets[[1]])$name)])
}

colnames(incidence_mats[[1]]) %in% V(igraph_nets[[1]])

```

```{try with bipartite}
# install.packages("bipartite")
library(bipartite)

test <- cbind(get.edgelist(sub_graph, names = T), as.numeric(E(sub_graph)$weight)) %>% as.tibble() %>%
  complete(V1 = sub_node[sub_node$sex == "M",]$unique_ID, V2 = sub_node[sub_node$sex == "F",]$unique_ID, fill = list(V3 = 0)) %>%
  filter(V1 != V2)
#test$V4 <- "trial"
colnames(test) <- c("lower","higher","freq","webID")
test <- test[,c("higher","lower","webID","freq")]

g <- graph.data.frame(test, directed = F)
V(g)$type <- V(g)$name %in% test$V2
E(g)$weight <- as.numeric(test$V3)
g

test_incidence <- get.incidence(g, attr = "weight")

# test2 <- frame2webs(test, varnames = c("higher","lower","webID","freq"), type.out = "array", emptylist = F)

par(mar = c(1,1,1,1))
plotweb(test_incidence, method = "normal", empty = F)
plotmatrix(test_incidence)

library(GGally)
library(ggbipart)
bip_net <- bip_init_network(test_incidence)
p <- bip_ggnet(bip_net, as.matrix(test_incidence), color = "mode", layout.exp = 0)

p +  geom_text(aes(label= network.vertex.names(bip_net)),
                        color= "black", size= 3) +
          theme(legend.position="none") 

g <- bip_railway(test_incidence, label = T)

g
install.packages("bipartiteD3")




```

## We have also started to take a look at some network-wide metrics. 

### *Density* = number of edges that exists divided by the total number of possible edges, so the number of matings our of all possible combinations of flies. 
### *Strength* = sum of the interactions for each fly. At this level, it would be the average number of matings for each fly in the network. 


```{r extract density and strengths}
library(assortnet)
#initialize a vector to store results in the loop, otherwise it will just write it over
densities <- rep(0, 25)
strengths <- rep(0, 25)
strengths_sd <- rep(0,25)
assort <- rep(0,25)
assort2 <- rep(0,25)
assort_poly <- rep(0,25)

#use a for loop to calculate densities and strengths
for(i in 1:25){
  sub <- rhag_edges[rhag_edges$trial_number == i,]
  sub_node <- rhag_nodes[rhag_nodes$trial_name == sub$trial_name,]
  sub <- sub %>% select(actor_uniqueID, receiver_uniqueID)
  sub_graph <- graph_from_data_frame(d = sub, vertices = sub_node$unique_ID, directed = T)
  E(sub_graph)$weight <- 1
  sub_graph <- simplify(sub_graph, edge.attr.comb=list(weight="sum"))
  V(sub_graph)$host <- ifelse(sub_node$host == "App","lightblue", "orange")
  sub_graph$strength <- strength(sub_graph)
  V(sub_graph)$strength <- sub_graph$strength
  densities[[i]] <- edge_density(sub_graph)
  #the ith value in our density vector we made earlier, put in the edge density for each network
  strengths[[i]] <- mean(strength(sub_graph))
  strengths_sd[[i]] <- sd(strength(sub_graph))
  sub_adj <- as_adjacency_matrix(sub_graph,  attr = "weight", sparse = F)
  assort[[i]] <- assortment.discrete(sub_adj, V(sub_graph)$host)$r
  assort2[[i]] <- assortativity_nominal(sub_graph, as.integer(as.factor(V(sub_graph)$host)), directed = F)
  assort_poly[[i]] <- assortment.discrete(sub_adj, V(sub_graph)$strength)$r
}  

#make a vector of trial names
trial_names <- unique(rhag_edges$trial_name)

#make a vector of temperatures
temp <- rep(c("control","warm"),times=c(10,15))

#combine into a data frame
global_summary <- data.frame(trial_names, temp, densities, strengths, strengths_sd, assort, assort2, assort_poly)

# ggplot(global_summary, aes(x = assort, y = assort2)) + geom_point()

ggplot(global_summary, aes(x = temp, y = densities)) + geom_boxplot() + geom_jitter() + ylab("Densities") + theme_bw()
t.test(global_summary[global_summary$temp == "control",]$densities, global_summary[global_summary$temp == "warm",]$densities)

ggplot(global_summary, aes(x = temp, y = strengths)) + geom_boxplot() + geom_jitter() + ylab("Strength aka Weighted Degree") + theme_bw()
t.test(global_summary[global_summary$temp == "control",]$strengths, global_summary[global_summary$temp == "warm",]$strengths)

ggplot(global_summary, aes(x = temp, y = strengths_sd)) + geom_boxplot() + geom_jitter() + ylab("Strength SD") + theme_bw()
t.test(global_summary[global_summary$temp == "control",]$strengths_sd, global_summary[global_summary$temp == "warm",]$strengths_sd)

ggplot(global_summary, aes(x = temp, y = assort2)) + geom_boxplot() + geom_jitter() + ylab("Assortativity by Host") + theme_bw()
t.test(global_summary[global_summary$temp == "control",]$assort2, global_summary[global_summary$temp == "warm",]$assort2)

ggplot(global_summary, aes(x = temp, y = assort_poly)) + geom_boxplot() + geom_jitter() + ylab("Assortativity by # mating partners") + theme_bw()
t.test(global_summary[global_summary$temp == "control",]$assort_poly, global_summary[global_summary$temp == "warm",]$assort_poly)

```

